---
title: Wave Properties
author: Dan Kelley
---

**NOTE:** looking only at equilibrium fetch-limitd case, so far.

**Test case**

``Example II-2-9'' in Chapter 2 of the Coastal Engineering Manual (2002): with
wind speed 30m/s and fetch 50km, significant wave height is 4.1m, while the
period at the spectral peak is 6.7s.

**Files in this directory**

```{r echo=FALSE}
source('00_formula.R')
u <- 30
x <- 50e3
```

* `00_formula.R` code patterned on example II-2-9 of CEM.  For the test case,
this yields as below
```{r}
waveProperties(30, 50e3)
```
* `01_model_selection.R` code to fit models to the critrion, the height, and
the period.  The (immeasurably small) misfits are shown in the top-left margins
of the three test panels. This also creates `01.rda`, for use later.

**References**
1. https://github.com/dankelley/sliderules/issues/2
2. U.S. Army Corps of Engineers. “Coastal Engineering Manual,” April 30, 2002. https://www.publications.usace.army.mil/USACE-Publications/Engineer-Manuals/u43544q/636F617374616C20656E67696E656572696E67206D616E75616C/.
